The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2014-12-04 draft.tex
MErged into one table

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Benchmark Model (Optimized for the UV Band) \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$R_{WD}$ 	 &	 $7\times10^{8}$cm\\ 
$T_{WD}$ 	 &	 $40,000$K\\
$M_{2}$ 	 &	 $0.4 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
%%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
$R_v$ 	        &	 $100 R_{WD}$ \\ 
$\alpha$ 	&	 $1.5$ \\
\end{tabular}
\centering
\caption{
Parameters used for the geometry and kinematics of the benchmark CV model.
{\bf JM: this needs some stuff adding, as is mentioned in certain places}}
\label{wind_param}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model B\\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $142.9 R_{WD}$ \\ 
$\alpha$ 	&	 $4$ \\
\end{tabular}
\centering
\caption{Wind geometry parameters used in the revised CV model, Model B,
which is {\em optimized for the optical band}
{\bf CK: I actually think we should probably have a single
table with both sets of model pars}}
\label{modelb_table}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{p{2cm}p{2cm}p{2cm}}
Model Parameters \\
\hline Parameter 	&	 Model A  & Model B \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$  &     \\ 
$R_{WD}$ 	 &	 $7\times10^{8}$cm  & \\ 
$T_{WD}$ 	 &	 $40,000$K        &  \\
$M_{2}$ 	 &	 $0.6 M_{\odot}$  &   \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-8}~M_{\odot}yr^{-1}$  &\\ 
$\dot{M}_{wind}$  &	$10^{-9}~M_{\odot}yr^{-1}$å  & \\ 
$r_{min}$ 	&	 $4 R_{WD}$ &  \\ 
$r_{max}$ 	&	 $12 R_{WD}$  &  \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$  &  \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$  &  \\ 
$\gamma$ 	&	 $1$  &  \\ 
$v_{\infty}$ 	&	 $3v_{esc}$  &  \\ 
%%$R_v$ 	        &	 $7\times10^{10}$cm \\ 
$R_v$ 	        &	 $100 R_{WD}$  &  $142.9 R_{WD}$  \\ 
$\alpha$ 	&	 $1.5$   &   $4$\\
\end{tabular}
\centering
\caption{
Parameters used for the geometry and kinematics of the benchmark 
CV model (Model A), which is optimized for the UV band, and a model
which is optimized for the optical band and described in section 6 (Model B).
For Model B, only parameters which are altered are given - otherwise the
Model A parameter is used.
{\bf JM: this needs some stuff adding, as is mentioned in certain places}}
\label{wind_param}
\label{modelb_table}
\end{table}

@@

% \begin{table}
% \centering
% \begin{tabular}{p{3cm}p{4cm}}
% Model B\\
% \hline Free Parameters 	&	 Value \\ 
% \hline \hline 
% $M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
% $\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
% $\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
% $r_{min}$ 	&	 $4 R_{WD}$\\ 
% $r_{max}$ 	&	 $12 R_{WD}$ \\ 
% $\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
% $\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
% $\gamma$ 	&	 $1$ \\ 
% $v_{\infty}$ 	&	 $3v_{esc}$ \\ 
% $R_v$ 	        &	 $142.9 R_{WD}$ \\ 
% $\alpha$ 	&	 $4$ \\
% \end{tabular}
% \centering
% \caption{Wind geometry parameters used in the revised CV model, Model B,
% which is {\em optimized for the optical band}
% {\bf CK: I actually think we should probably have a single
% table with both sets of model pars}}
% \label{modelb_table}
% \end{table}
